Analysis-ready VCF at Biobank scale using Zarr

### 2025-01-30 paper.tex
Add region index text

>>>>

To facilitate efficient region search queries, we compute an
additional array \texttt{region\_index} which stores information
about the range of genomic positions in each chunk
and provides sufficient information to implement interval
search queries. We can then load this index into memory and 
use it to determine which variant chunks need to be retrieved.
In the Norway Spruce example (Table~\ref{tab-spruce-data}),
which has 3.75 billion variants,
this index requires 3.14 MiB of storage over 12 chunk files
to store information about all 
374,518 variant chunks 
(the \texttt{variant\_position} array, for comparison 
is 13.95 GiB uncompressed).
